True versus apparent shapes of astrophysical bow shocks

### 2017-04-25 papers/Paper1/quadrics-appendix.tex
Column descriptions for Table E1

% Landscape table needs to go on its own page, so we need to manually
% adjust the section counter so that it will ``belong'' to the next
% section
\addtocounter{section}{1}
\sisetup{detect-all=true, detect-inline-weight=math}
\sisetup{round-mode=figures, round-precision=2}
\begin{landscape}
\begin{table}
  \setlength\tabcolsep{3pt}
  \caption{Results of all statistical tests performed on observed bow shock shape parameters. Significant correlations are shown in \textbf{bold}, marginally significant correlations in \textit{italic}}
  \label{tab:big-p}
  \input{figs/mipsgal-summary-stats-table-body.tex}
\end{table}
\end{landscape}
\addtocounter{section}{-1}

\section{Distribution of p-values for all correlations tested}
\label{sec:distr-p-values}

>>>>

% Landscape table needs to go on its own page, so we need to manually
% adjust the section counter so that it will ``belong'' to the next
% section
\addtocounter{section}{1}
\sisetup{detect-all=true, detect-inline-weight=math}
\sisetup{round-mode=figures, round-precision=2}
\begin{landscape}
\begin{table}
  \setlength\tabcolsep{3pt}
  \caption{Results of all statistical tests performed on observed bow shock shape parameters. Significant correlations are shown in \textbf{bold}, marginally significant correlations in \textit{italic}}
  \label{tab:big-p}
  \input{figs/mipsgal-summary-stats-table-body.tex}
\end{table}
\end{landscape}
\begin{table}
  \contcaption{Results of all statistical tests performed on observed
    bow shock shape parameters.}
  \begin{tabular}{p{0.9\linewidth}}
    \toprule
    \textit{Description of columns:}
    (Col.~1)~How the two A/B source sub-samples are defined, also giving the size of each sub-sample, \(n_{\text{A}}\) and~\(n_{\text{B}}\).
    (Col.~2)~Dependent variable whose distribution is compared between the two sub-samples.
    (Cols.~3--6)~Mean and standard deviation, \(\sigma\), of the dependent variable for each of the two sub-samples.
    (Cols.~7--8)~Mean over each sub-sample of the observational dispersion (\(\epsilon\), standard deviation) of radii that contribute to the dependent variable for each individual source.
    (Cols.~9--10)~``Standard error of the mean'' (s.e.m.) of the dependent variable for each of the two sub-samples. 
    (Cols.~11--13)~Standardized ``effect sizes'', which are dimensionless measures of the difference in the distribution of the dependent variable between the two sub-samples.
    (Col.~11)~Rank biserial correlation coefficient \citep{Cureton:1956a}, which is obtained by considering all \(n_{\text{A}} n_{\text{B}}\) pair-wise comparisons of the dependent variable between a source in sub-sample~A and a source in sub-sample~B.  It is the difference between the fraction of such comparisons ``won'' by sub-sample~A and those ``won'' by sub-sample~B, and thus may vary between \(-1\) and \(+1\). 
    (Col.~12)~Cohen's \(d\), which is a dimensionless mean difference: \(d = (\langle \text{A} \rangle - \langle \text{B} \rangle) / \sigma_{\text{pool}} \), where \(\sigma_{\text{pool}} = (n_{\text{A}} \sigma_{\text{A}}^2 + n_{\text{B}} \sigma_{\text{B}}^2)^{1/2} / \sqrt{n_{\text{A}} + n_{\text{B}}}\) is the pooled standard deviation.
    (Col.~13)~Ratio of standard deviations between the two sub-samples.
    (Cols.~14--16)~Probabilities (\(p\)-values) of the two sub-samples being as different as observed if they were to be drawn from the same population, according to three different non-parametric tests.
    (Col.~14)~Anderson--Darling 2-sample test, which is a general test of similarity between two distributions that is designed to retain sensitivity to differences in the tails of the distributions.
    (Col.~15)~Mann--Whitney--Wilcoxon \(U\) test \citep{Mann:1947a}
    (Col.~16)~Brown--Forsythe test for dispersion
    \\
    \bottomrule
  \end{tabular}
\end{table}

\addtocounter{section}{-1}

\section{Distribution of p-values for all correlations tested}
\label{sec:distr-p-values}
\addtocounter{table}{1}
